heatmap

### 2020-01-22 analysis/17_pheatmap.Rmd
meh, heatmaps

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pheatmap)

@@

```{r, pheatmap, fig.height=6.5}
prepvsds <- function(pathtofile){

@@

  df <- tail(df, 5000)
  df <- head(df, 1000)

@@

@@

pheatmap(vsd.hyp, show_colnames = F, annotation_col = hyplabels, 
         annotation_colors = myannotationcolors, show_rownames = F)
pheatmap(vsd.pit, show_colnames = F, annotation_col = pitlabels, 
         annotation_colors = myannotationcolors, show_rownames = F)
pheatmap(vsd.gon, show_colnames = F, annotation_col = gonlabels, 
         annotation_colors = myannotationcolors, show_rownames = F)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pheatmap)

@@

```{r, pheatmap, fig.height=6.5}
calisigenes <- c("PRL", "PRLR", 
                 "VIP", "VIPR1", "VIPR2", 
                 "OXT", "AVP", "AVPR1A", "AVPR1B", 
                 "GNRH1","GNRHR", "NPVF",
                 "NR3C1", "NR3C2",
                 "ESR1", "ESR2", "AR")

prepvsds <- function(pathtofile){

@@

@@

  df <- as.data.frame(df)
  df$gene <- row.names(df)
  df <- df %>% dplyr::filter(gene %in% calisigenes)
  df <- as.data.frame(df)
  row.names(df) <-  df$gene
  df$gene <- NULL

@@

pheatmap(vsd.hyp, show_colnames = F, annotation_col = hyplabels, 
         annotation_colors = myannotationcolors, show_rownames = T)
pheatmap(vsd.pit, show_colnames = F, annotation_col = pitlabels, 
         annotation_colors = myannotationcolors, show_rownames = T)
pheatmap(vsd.gon, show_colnames = F, annotation_col = gonlabels, 
         annotation_colors = myannotationcolors, show_rownames = T)

```
